Figures for conference paper

### 2019-05-22 conference figures COPA2019.Rmd
create plots and table for results of conformal prediction

load("Output/app_model.RDATA")
load("Output/data_pillar_1.Rdata")
load("Output/d_text.RDATA")
load("Output/df_logLike_catalogue.RDATA")
load("Output/CV.RDATA")

@@

@@

```{r}
course_data <- d_text$catalogues %>%

@@

```{r}
latex_table <- function(df, filename = "test"){

@@

```{r}
grViz("digraph flowchart{

@@

@@

@@

  beta %>%
    filter(topic == top) %>% 
    top_n(10, beta) %>%

    ggplot() +
    geom_col(aes(x = reorder(term, beta), y = beta)) +

@@

    labs(title = NULL,
         x = "Terms",
         y = "Beta"
         )

  ggsave(filename = str_c("Beta-", topic, ".jpeg"), path = output_folder,
         width = plot_width / resize_factor, height = plot_height / resize_factor)

@@

resize_factor <- 2

plot_beta(4, resize_factor = resize_factor)
plot_beta(19, resize_factor = resize_factor)
```

@@

transcript <- tibble(Course    = courses,
                     Grade     = c(6  , 9  , 2.5))

@@

topic_expertise <- df1 %>%
  select(-gamma, - Grade) %>% 
  spread(key = Topic, value = contribution)

@@

# Plot
df1 %>% 
  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
  geom_col() +
  coord_flip() +
  labs(x = "Topics", y = "Topic Expertise")

@@

>>>>

load("Output/app_model.RDATA")
load("Output/data_pillar_1.Rdata")
load("Output/d_text.RDATA")
load("Output/df_logLike_catalogue.RDATA")
load("Output/CV.RDATA")
load("Output/conformal.RDATA")

@@

```{r latex_table}
latex_table <- function(df, filename = "test"){

@@

```{r course_data}
course_data <- d_text$catalogues %>%

@@

@@

## EDM2019 style
```{r}
grViz("digraph flowchart{

@@

## 2 pillar style
```{r}
grViz("digraph flowchart{

      fontname = Helvetica
      size = 15
      newrank = true;

      node [fontname = Helvetica, shape = rectangle, style = filled, fillcolor = white]
      edge [fontname = Helvetica, decorate = TRUE]

      subgraph cluster_input_kw {
      label = 'User Input';
      penwidth = 2;

      KW [label = 'Selected Key Words']
      }

      subgraph cluster_data {
      label = 'Data';
      penwidth = 2;

		  node [shape = cylinder];
      SD [label = 'Student Data', group = 2]
      CD [label = 'Course Data' , group = 1]
      }

      subgraph cluster_input_course {
      label = 'User Input';
      penwidth = 2;

      CS [label = 'Selected Courses']
      }

      subgraph cluster_pillar_1{
      label = 'Pillar 1: Course Suggestion';
      penwidth = 2;

      TM  [label = 'Topic Model \nof the Courses', group = 1]
      AI  [label = 'Model of \nStudent´s Academic Interests']
      x1  [shape = circle, width = .01, height = .01, label = '']
      SUG [label = 'Course Suggestions', ]

      } # close pillar 1

      subgraph cluster_pillar_2{
      label = 'Pillar 2: Warning Issuance';
      penwidth = 2;

      SM  [label = 'Student Model'    , group = 2]
      PM  [label = 'Predictive Models', group = 2]
      GP  [label = 'Point Prediction \nfor Grade' , group = 2]
      WAR [label = 'Warning'          , group = 2]
      PR  [label = 'Prediction Region', color = red, fontcolor = red]

      } # close pillar 2

		  { rank=same; KW; CD; SD; CS}
		  { rank=same; TM; SM}
      { rank=same; PR; WAR; SUG}

      # edges
      CD -> TM [label = '  LDA'];
      {TM, KW} -> AI;
      {TM, AI} -> x1 [arrowhead = none]
      x1 -> SUG [label = '  KL distance'];

      SD -> SM;
      TM -> SM;
      SM -> PM [label = '  Lasso'];
      {PM, CS} -> GP;
      GP -> WAR;
      GP -> PR [label = ' Conformal Prediction', color = red, fontcolor = red];

@@

```{r reorder_within}
reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}

scale_y_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
}
```

@@

  beta %>%
    filter(topic %in% top) %>% 
    group_by(topic) %>%
    top_n(9, beta) %>%

    ggplot() +
    geom_col(aes(x = reorder_within(term, beta, topic), y = beta)) +

@@

    labs(title = NULL, x = "Terms", y = "Beta") +

    facet_wrap( ~ topic, scales = "free_y") +
    scale_x_reordered()

  ggsave(filename = "beta.jpeg", path = output_folder,
         width = 1.5 * plot_width / resize_factor, height = plot_height / resize_factor)

@@

resize_factor <- 1.8

plot_beta(c(4,19), resize_factor = resize_factor)
```

@@

transcript <- tibble(Course    = courses,
                     Grade     = c(6  , 9  , 2))

@@

topic_expertise <- df1 %>%
  select(-gamma, - Grade)%>% 
  spread(key = Topic, value = contribution) %>%
  add_row(Course = "Total", `Topic 1` = 0.18, `Topic 2` = 0.68, `Topic 3` = 0.34, `Topic 4` = 0.26, `Topic 5` = 0.22)

@@

# Plot
df1 %>% 
  mutate(Topic = factor(Topic, levels = str_c("Topic ", 5:1))) %>%
  ggplot(aes(x = Topic, y = contribution, fill = Course)) +
  geom_col() +
  coord_flip() +
  labs(x = "Topics", y = "Topic Expertise")

@@

# Conformal

## course table

```{r}
course_table %>%
  select(- df) %>%
  mutate(cv_error = cv_error %>% round(2)) %>%
  latex_table("conformal-course")
```

## width

```{r}
d_width <- conformal_results %>%
  group_by(course, significance) %>%
  summarise(q_50 = quantile(width, 0.5), # median
            q_10 = quantile(width, 0.1),
            q_90 = quantile(width, 0.9))
```

```{r}
d_width %>%
  ggplot() +
  geom_errorbar(aes(significance, ymax = q_90, ymin = q_10), size = .5) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_line(aes(significance, q_50, group = 1)) +
  geom_point(aes(significance, q_50)) +
  facet_wrap( ~ course) +
  labs(y = "Width",
       x = "Significance Level") +
  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8))

ggsave(filename = "conformal-width.jpeg", path = output_folder,
       width = plot_width, height = plot_height)
```

## Error

```{r}
d_error <- conformal_results %>%
  group_by(course, significance) %>%
  summarise(error = mean(!hit))
```

```{r}
d_error %>%
  ggplot(aes(x = significance, y = error)) +
  geom_abline(slope = 1, linetype = "longdash") +
  geom_line(aes(group = 1)) +
  geom_point() +
  facet_wrap( ~ course) +
  labs(y = "Error Rate",
       x = "Significance Level") +
  scale_x_continuous(breaks = c(0.05, 0.2, 0.4, 0.6, 0.8))

ggsave(filename = "conformal-error.jpeg", path = output_folder,
       width = plot_width, height = plot_height)
```

## Table
```{r}
conformal_results %>%
  filter(significance %in% c(0.05, 0.1, 0.2)) %>%
  group_by(course, significance) %>%
  summarize(width_med  = median(width),
            error_rate = mean(!hit)) %>%

  gather(key = "measure", value = "output", width_med, error_rate) %>%
  mutate(output = round(output, 2)) %>%
  unite(id, measure, significance, sep = "-") %>%
  spread(key = id, value = output) %>%

  select(course, matches("med"), matches("error")) %>%
  latex_table("conformal-table")
```
